A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-15 6_validation.tex
redo analysis figures

\begin{figure}
\includegraphics[width=\columnwidth]{sources/validation/overunderfill.pdf}
\caption{total over and underfill for entire dataset}
\label{over_underfill}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{sources/validation/smoothness.pdf}
\caption{occurrence of angles between consecutive segments}
\label{smoothness}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{sources/validation/widthHistogram.pdf}
\caption{Distribution of extrusion width, sampled at  \SI{200}{\micro\meter}, visualized data is binned at intervals of  \SI{10}{\micro\meter}}
\label{widthHistogram}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{sources/validation/computime2.pdf}
\caption{Computation time per slice}
\label{computime}
\end{figure}

@@

To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
at intervals of \SI{200}{\micro\meter} along the toolpath.
From these sampled values, we calculated the mean bead width, and standard deviation.
\cref{widthHistogram} shows the distribution of extrusion width for each strategy.
The results show that the mean width of our strategies "Inwards distributed" and "Evenly distributed" is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies "Centered" and "Constant bead count". 
These values indicate that, while causing less overfill and underfill, our strategy deviates less and less often from the nominal nozzle size.

>>>>

\begin{figure*}
\centering
\setlength{\figheight}{0.2\textwidth}
\setlength{\figwidth}{0.24\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/computime2.pdf}
%\includegraphics[width=\figwidth]{sources/validation/computime2.pdf}
\caption{Computation time and target vertex count for the full dataset}
\label{computime}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/overunderfill.pdf}
%\includegraphics[width=\figwidth]{sources/validation/overunderfill.pdf}
\caption{Total over and underfill area}
\label{over_underfill}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/widthHistogram.pdf}
%\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
\caption{Relative frequency of extrusion widths}
\label{widthHistogram}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/smoothness.pdf}
%\includegraphics[width=\figwidth]{sources/validation/smoothness.pdf}
\caption{Frequency of angles between consecutive segments}
\label{smoothness}
\end{subfigure}
\caption{Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the dataset.}
\end{figure*}

@@

To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
at intervals of \SI{200}{\micro\meter} along the toolpath.
From these sampled values, we calculated the mean bead width, and standard deviation.
\cref{widthHistogram} shows the distribution of extrusion width for each strategy binned at intervals of  \SI{10}{\micro\meter}.
The results show that the mean width of our strategies "Inwards distributed" and "Evenly distributed" is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies "Centered" and "Constant bead count". 
These values indicate that, while causing less overfill and underfill, our strategy deviates less and less often from the nominal nozzle size.
